\article{Nebular \lbrack Fe II\rbrack\ emission as a constraint on Type Ia supernova progenitors}
{\highlight{L. Shingles}, Stuart Sim, Andreas Floers, et al.}{Monthly Notices of the Royal Astronomical Society, (2021, in preparation).}

\article{\href{https://ui.adsabs.harvard.edu/abs/2020MNRAS.499.4312K/abstract}{The influence of line opacity treatment in STELLA on supernova light curves}}
{A. Kozyreva, \highlight{L. Shingles}, Alexey Mironov, Petr Baklanov, Sergey Blinnikov}
{Monthly Notices of the Royal Astronomical Society, Volume 499, Issue 3, pp.4312-4324 (2020).}

\article{\href{https://ui.adsabs.harvard.edu/abs/2020MNRAS.492.2029S}{Monte Carlo radiative transfer for the nebular phase of Type Ia supernovae}}
{\highlight{L. Shingles}, S. A. Sim, M. Kromer, K. Maguire, M. Bulla, C. Collins, C. P. Ballance, A. S. Michel, C. A. Ramsbottom, F. K. R\"opke, I. R. Seitenzahl, N. B. Tyndall}
{Monthly Notices of the Royal Astronomical Society, Volume 492, Issue 2, p.2029-2043 (2020).}

\article{\href{https://ui.adsabs.harvard.edu/abs/2019NatAs.tmp..463G}{A year-long plateau in the late-time near-infrared light curves of Type Ia supernovae}}
{Or Graur, Kate Maguire, Russell Ryan, Matt Nicholl, Arturo Avelino, Adam G. Riess, \highlight{Luke Shingles}, Ivo R. Seitenzahl, and Robert Fisher}
{Nature Astronomy, Advanced Online Publication (2019).}

\article{\href{http://adsabs.harvard.edu/abs/2018MNRAS.477.3567M}{Using late-time optical and near-infrared spectra to constrain Type Ia supernova explosion properties}}
{K. Maguire, S. A. Sim, \highlight{L. Shingles}, J. Spyromilio, A. Jerkstrand, M. Sullivan, T.-W. Chen, R. Cartier, G. Dimitriadis, C. Frohmaier, L. Galbany, C. P. Gutiérrez, G. Hosseinzadeh, D. A. Howell, C. Inserra, R. Rudy, J. Sollerman}
{Monthly Notices of the Royal Astronomical Society, Volume 477, Issue 3, p.3567-3582 (2018).}

\article{\href{http://adsabs.harvard.edu/abs/2017Natur.551...75S}{A kilonova as the electromagnetic counterpart to a gravitational-wave source}}
{S. J. Smartt, T.-W. Chen, A.Jerkstrand, M. Coughlin, E. Kankare, S. A. Sim, M. Fraser, C. Inserra, K. Maguire, K. C. Chambers,
M. E. Huber, T. Kr\"uhler, G. Leloudas, M. Magee, \highlight{L. J. Shingles}, and 107 additional authors}
{Nature, Volume 551, Issue 7678, pp. 75-79 (2017)}

\article{\href{http://adsabs.harvard.edu/abs/2017ApJ...848L..12A}{Multi-messenger Observations of a Binary Neutron Star Merger}}
{Joint-authored by several collaborations including ePESSTO (including \highlight{L. J. Shingles})}
{The Astrophysical Journal Letters, Volume 848, Issue 2, article id. L12, 59 pp. (2017).}

\article{\href{http://adsabs.harvard.edu/abs/2017ApJ...837..176Y}{A chemical signature from fast-rotating low-metallicity massive stars: ROA 276 in omega Centauri}}
{David Yong, John E. Norris, Gary S. Da Costa, Laura M. Stanford, Amanda I. Karakas, \highlight{Luke J. Shingles}, Raphael Hirschi, Marco Pignatari}
{The Astrophysical Journal, Volume 837, Issue 2, article id. 176, 8 pp. (2017).}

\article{\href{http://adsabs.harvard.edu/abs/2015MNRAS.452.2804S}{Evolution and nucleosynthesis of helium-rich asymptotic giant branch models}}
{\highlight{Luke J. Shingles}, Carolyn L. Doherty, Amanda I. Karakas, Richard J. Stancliffe, John C. Lattanzio, Maria Lugaro}
{Monthly Notices of the Royal Astronomical Society, Volume 452, Issue 3, p.2804-2821 (2015).}

\article{\href{http://adsabs.harvard.edu/abs/2015MNRAS.450..815M}{Iron and s-element abundance variations in NGC 5286: comparison with anomalous' globular clusters and Milky Way satellites}}
{A. F. Marino, A. P. Milone, A. I. Karakas, L. Casagrande, D. Yong, \highlight{L. Shingles}, G. Da Costa, J. Norris, P. B. Stetson,  K. Lind, M. Asplund, R. Collet, H. Jerjen, L. Sbordone, A. Aparicio, \& S. Cassisi}
{Monthly Notices of the Royal Astronomical Society, Volume 450, Issue 1, p.815-845 (2015).}

\article{\href{http://adsabs.harvard.edu/abs/2014ApJ...795...34S}{The s-process enrichment of the globular clusters M4 and M22}}
{\highlight{Luke J. Shingles}, Amanda I. Karakas, Raphael Hirschi, Cherie K. Fishlock, David Yong, Gary S. Da Costa, \& Anna F. Marino}
{The Astrophysical Journal, Volume 795, Issue 1, article id. 34, 12 pp. (2014).}

\article{\href{http://adsabs.harvard.edu/abs/2014MNRAS.441.3396Y}{Iron and neutron-capture element abundance variations in the globular cluster M2 (NGC 7089)}}
{David Yong, Ian U. Roederer, Frank Grundahl, Gary S. Da Costa, Amanda I. Karakas, John E. Norris, Wako Aoki, Cherie K. Fishlock, A. F. Marino, A. P. Milone, \& \highlight{Luke J. Shingles}}
{Monthly Notices of the Royal Astronomical Society, Volume 441, Issue 4, p.3396-3416 (2014).}

\article{\href{http://adsabs.harvard.edu/abs/2013Ap\%26SS.347...47V}{Augmented reality in astrophysics}}
{Fr\'{e}d\'{e}ric Vogt \& \highlight{Luke J. Shingles}}
{Astrophysics and Space Science, Volume 347, Issue 1, pp.47-60 (2013).}

\article{\href{http://adsabs.harvard.edu/abs/2013MNRAS.431.2861S}{Is the sulphur anomaly in planetary nebulae caused by the s-process?}}
{\highlight{Luke J. Shingles} \& Amanda I. Karakas}
{Monthly Notices of the Royal Astronomical Society, Volume 431, Issue 3, p.2861-2871 (2013).}

